Climate Prediction Markets and Convergence of Predictive Models

### 2015-06-15 prediction_market.Rnw
caption for temporal evolution figure

>>>>

\begin{figure}
\centering
<<temporal, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE, fig.width=10, fig.height=6>>=
sample_count <- 1000
load("output/average_convergence.Rda")
dat <- average_convergence[average_convergence$true_mod != "Both", ]
dat$true_mod <- factor(dat$true_mod, levels = c("Natural", "Human-Induced"), 
                       labels = c("Natural Change", "Human-Induced"))
library(ggplot2)
ggplot(data= dat, aes(x= trading_seq, y=avg, color = true_mod)) +
  geom_smooth(method = "loess") + 
  ggtitle("Average Convergence Over Trading Sequences") +
  xlab("Trading Sequences") + 
  ylab(paste0("Average Convergence (n = ", formatC(sample_count, big.mark = ','), ")")) + 
  theme_bw() + theme(legend.justification=c(0,1), legend.position=c(0,1)) + 
  scale_color_discrete(name="True Model")
@
\caption{Temporal evolution of convergence of beliefs for the ABM with \Sexpr{formatC(sample_count, big.mark=',')} model runs with ``True Model'' parameter set to natural climate change and \Sexpr{formatC(sample_count, big.mark=',')} model runs with ``True Model'' parameter set to human-induced climate change. All other parameters are sampled from their full support with Latin Hypercube Sampling; therefore, the plot represents, in effect, a marginalizing out of the effects of all other parameters to show the moderating effect that the true model has on the effect of the prediction market on the convergence of traders' beliefs about what the true model is. The prediction market causes opposite convergence effects for the two true climate models.}
\label{fig:temporal}
\end{figure}

### 2015-06-15 prediction_market.tex
caption for temporal evolution figure

\end{knitrout}
\caption{Temporal evolution of convergence of beliefs.}
\label{fig:temporal}
\end{figure}

>>>>

\end{knitrout}
\caption{Temporal evolution of convergence of beliefs for the ABM with 1,000 model runs with ``True Model'' parameter set to natural climate change and 1,000 model runs with ``True Model'' parameter set to human-induced climate change. All other parameters are sampled from their full support with Latin Hypercube Sampling; therefore, the plot represents, in effect, a marginalizing out of the effects of all other parameters to show the moderating effect that the true model has on the effect of the prediction market on the convergence of traders' beliefs about what the true model is. The prediction market causes opposite convergence effects for the two true climate models.}
\label{fig:temporal}
\end{figure}
